Modelling circumstellar discs with 3D radiation hydrodynamics

### 2009-10-12 SPH-Torus-paper1/sphtorus_benchmark.tex
Minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2052 25464f21-6099-402c-b30a-640f1d40d38b

The frequency with which the radiative transfer is calculated is
determined by the sound crossing time in the inner regions of the disc
as this is the time scale over which the scale height in this region
will vary and effect the transfer of radiation into the outer parts of
the disc.  The vertical sound crossing time at a radius of
10\,au is typically 2 years, so a radiative transfer calculation is
performed after every four hydrodynamics time steps (equivalent to
every 2.4 years).

>>>>

The frequency with which the radiative transfer is calculated is
determined by the sound crossing time in the inner regions of the disc
as this is the time scale over which the scale height in this region
will vary and effect the transfer of radiation into the outer parts of
the disc.  The vertical sound crossing time at a radius of
10\,au is typically approximately 2 years, so a radiative transfer calculation is
performed after every four hydrodynamics time steps (equivalent to
every 2.4 years).
